---
title: "renderthis setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

To get the most out of renderthis, we recommend installing the package
**with dependencies** and making sure that you have a local installation
of Chrome.

# Installation

You can install the latest version of renderthis from
[CRAN](https://cran.r-project.org/) with:

```{r}
install.packages("renderthis")
```

And the development version from GitHub with:

```{r}
# install.packages("remotes")
remotes::install_github("jhelvy/renderthis")
```

Some output formats require additional packages, and each format will provide
instructions about how to install any missing dependencies. You can also
choose to install renderthis with all of its dependencies:

```{r}
# From CRAN
install.packages("renderthis", dependencies = TRUE)

# From GitHub
remotes::install_github("jhelvy/renderthis", dependencies = TRUE)
```

# Local Chrome Installation

Rendering the PDF requires a local installation of Chrome. If you don't have
Chrome installed, you can use other browsers based on Chromium, such as
Chromium itself, Edge, Vivaldi, Brave, or Opera. In this case, you will need
to set the path to the browser you want to use for the
[pagedown](https://github.com/rstudio/pagedown) package as well as the
[chromote](https://github.com/rstudio/chromote) package if you use the
`complex_slides = TRUE` or `partial_slides = TRUE` arguments.

After installing the packages, you can set the paths like this:

```{r, eval=FALSE}
Sys.setenv(PAGEDOWN_CHROME = "/path/to/browser")
Sys.setenv(CHROMOTE_CHROME = "/path/to/browser")
```

If you're not sure where Chrome lives on your machine,
try the following command to search for it:

```{r, eval=FALSE}
pagedown::find_chrome()
```

If you are unable to install Chrome (e.g. on a computing cluster), the
recommended workflow is to render intermediate output formats and use an
alternative method for rendering the PDF.

For example, to render a pptx from a Rmd file without Chrome, you could:

1. Render the html with `to_html(from = "slides.Rmd")`
2. Use vscode remote and vscode-preview-server extension to open the html on a local machine (preferrably with Chrome installed)
3. Save to pdf on Chrome
4. Render the pptx with `to_pptx(from = "slides.pdf")`

# Dependencies

Because many users will not need all output formats,
several outputs require additional packages that are suggested dependencies
and aren't installed by default unless requested as described above.
The table below lists the packages required for each output type:

| Output | Requires |
|:-----|:-----|
| PDF (simple) | Google Chrome (for [pagedown](https://pagedown.rbind.io/)) |
| PDF (complex) | [chromote](https://rstudio.github.io/chromote/) |
| PNG | Requires PDF |
| GIF | Requires PDF |
| MP4 | [av](https://docs.ropensci.org/av/) |
| PPTX | [officer](https://ardata-fr.github.io/officeverse/) |
| Social | [webshot2](https://rstudio.github.io/webshot2/) |
